Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1 and ERC project 280053 (CPROVER).}

### 2017-02-01 hscc2017/paper.tex
Added missing benchmark
Added missing tapedriver benchmark.

\begin{table}
\centering
\begin{tabular}{| r | c | l | r r || r | r |}
\hline
\# & Plant  & Benchmark                  & $I$ & $F$
   & 1-step & 2-step
    \\\hline\hline
1  & $G_1$  & CrsControl02
            &   4 &  16 & 12\,s   & 67\,s     \\
2  & $G_1$  & CrsControl02$^\dagger$
            &   4 &  16 & 14600\,s   & 52\,s     \\
3  & $G_2$  & SpgMsDamper
            &  15 &  16 & 52\,s   & 318\,s     \\
4  & $G_2$  & SpgMsDamper$^\dagger$
            &  15 &  16 & \xmark  & \xmark    \\
5  & $G_3$  & SatelliteB2
            &   3 &   7 & 36,s    & \xmark     \\
6  & $G_3$  & SatelliteB2$^\dagger$
            &   3 &   7 & \xmark  & 4111\,s  \\
7  & $G_3$  & SatelliteC2
            &   3 &   5 & 3\,s    & 205\,s    \\
8  & $G_3$  & SatelliteC2$^\dagger$
            &   3 &   5 & 50\,s  & 1315\,s    \\
9  & $G_3$  & Cruise
            &   3 &   7 & 1\,s  & 1\,s    \\
10 & $G_3$  & DC Motor
            &   3 &   7 & 1\,s  & 10\,s    \\
11 & $G_3$  & DC servomotor
            &   4 &  11 & 46\,s  & \xmark    \\
12 & $G_3$  & Doyleetal
            &   4 &  11 & 8769\,s  & \xmark    \\
13 & $G_3$  & Helicopter
            &   3 &   7 & 44\,s  & \xmark    \\
14 & $G_3$  & Pendulum
            &   3 &   7 & 1\,s  & 14826\,s    \\
15 & $G_3$  & Suspension
            &   3 &   7 & 1\,s  & 5\,s    \\
16 & $G_4a$ & a\_ST1\_IMPL1
            &  16 &   4 & 11748\,s & \xmark   \\
17 & $G_4a$ & a\_ST1\_IMPL2
            &  16 &   8 & 351\,s  & \xmark   \\
18 & $G_4a$ & a\_ST1\_IMPL3
            &  16 &  12 & 8772\,s   & \xmark   \\
19 & $G_4b$ & a\_ST2\_IMPL1
            &  16 &   4 & 1128\,s  & \xmark   \\
20 & $G_4b$ & a\_ST2\_IMPL2
            &  16 &   8 & \xmark  & \xmark    \\
21 & $G_4b$ & a\_ST2\_IMPL3
            &  16 &  12 & 15183\,s & \xmark   \\ 
22 & $G_4c$ & a\_ST3\_IMPL1
            &  16 &   4 & \xmark & \xmark   \\\hline
\end{tabular}

@@

The median runtime for our benchmark set is $50$\,s, implying that \tool
can synthesize half of the controllers in less than one minute.  Overall,
the average synthesis time amounts to approximately $45$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $18$ out of the $22$ benchmarks, and can be complemented using the
one-stage engine for additional benchmarks, where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $19$ out of $22$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers were confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2.
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}\footnote{CBMC version: \url{https://github.com/diffblue/cbmc/archive/7a6cec1dd0eb8843559591105235f1f2c4678801.zip}}

>>>>

\begin{table}
\centering
\begin{tabular}{| r | c | l | r r || r | r |}
\hline
\# & Plant  & Benchmark                  & $I$ & $F$
   & 1-step & 2-step
    \\\hline\hline
1  & $G_1$  & CrsControl02
            &   4 &  16 & 12\,s   & 67\,s     \\
2  & $G_1$  & CrsControl02$^\dagger$
            &   4 &  16 & 14600\,s   & 52\,s     \\
3  & $G_2$  & SpgMsDamper
            &  15 &  16 & 52\,s   & 318\,s     \\
4  & $G_2$  & SpgMsDamper$^\dagger$
            &  15 &  16 & \xmark  & \xmark    \\
5  & $G_3$  & SatelliteB2
            &   3 &   7 & 36,s    & \xmark     \\
6  & $G_3$  & SatelliteB2$^\dagger$
            &   3 &   7 & \xmark  & 4111\,s  \\
7  & $G_3$  & SatelliteC2
            &   3 &   5 & 3\,s    & 205\,s    \\
8  & $G_3$  & SatelliteC2$^\dagger$
            &   3 &   5 & 50\,s  & 1315\,s    \\
9  & $G_4$  & Cruise
            &   3 &   7 & 1\,s  & 1\,s    \\
10 & $G_5$  & DC Motor
            &   3 &   7 & 1\,s  & 10\,s    \\
11 & $G_6$  & DC servomotor
            &   4 &  11 & 46\,s  & \xmark    \\
12 & $G_7$  & Doyleetal
            &   4 &  11 & 8769\,s  & \xmark    \\
13 & $G_8$  & Helicopter
            &   3 &   7 & 44\,s  & \xmark    \\
14 & $G_9$  & Pendulum
            &   3 &   7 & 1\,s  & 14826\,s    \\
15 & $G_10$  & Suspension
            &   3 &   7 & 1\,s  & 5\,s    \\
16 & $G_11$  & Tapedriver
            &   3 &   7 & 1\,s  & 1\,s    \\
17 & $G_12a$ & a\_ST1\_IMPL1
            &  16 &   4 & 11748\,s & \xmark   \\
18 & $G_12a$ & a\_ST1\_IMPL2
            &  16 &   8 & 351\,s  & \xmark   \\
19 & $G_12a$ & a\_ST1\_IMPL3
            &  16 &  12 & 8772\,s   & \xmark   \\
20 & $G_12b$ & a\_ST2\_IMPL1
            &  16 &   4 & 1128\,s  & \xmark   \\
21 & $G_12b$ & a\_ST2\_IMPL2
            &  16 &   8 & \xmark  & \xmark    \\
22 & $G_12b$ & a\_ST2\_IMPL3
            &  16 &  12 & 15183\,s & \xmark   \\ 
23 & $G_12c$ & a\_ST3\_IMPL1
            &  16 &   4 & \xmark & \xmark   \\\hline
\end{tabular}

@@

The median runtime for our benchmark set is $48$\,s, implying that \tool
can synthesize half of the controllers in less than one minute.  Overall,
the average synthesis time amounts to approximately $42$ minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  We further observe that the approach using
the two-stage verification engine is able to synthesize stable controllers
in $19$ out of the $23$ benchmarks, and can be complemented using the
one-stage engine for additional benchmarks, where the inductive
conjectures fail.  Both verification engines together enable controller
synthesis for $20$ out of $23$ benchmarks.  For the remaining benchmarks
our approach failed to synthesize a stable controller within the time
limits.  This can be addressed by either increasing either the time limit
or the fixed-point word widths considered, or by using floating-point
arithmetic instead.  The synthesized controllers were confirmed to be stable
outside of our model representation using MATLAB, positively answering RQ2.
A~link to the full experimental environment, including scripts to reproduce
the results, all benchmarks and the \tool tool, is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}\footnote{CBMC version: \url{https://github.com/diffblue/cbmc/archive/7a6cec1dd0eb8843559591105235f1f2c4678801.zip}}
